Bioverse: Origins of Life

### 2023-12-12 src/tex/ms.tex
split methods into semi-analytical analysis and Bioverse

\subsection{H3: Life only originates on planets with particular UV irradiance}
\todo[inline]{\citet{Guenther2020} relate U-band energy to bolometric flux.}
\todo[inline]{OPTIONAL: ``We further test the scenario of a linear correlation of past UV flux and biosignature occurrence rate.
This test requires the detection of multiple biosignatures.''
~\\
Test for negative correlations as well?}
Our third theoretical experiment is to test the UV irradiance requirement (Sect.~\ref{sec:predictions:uv}) by relating the occurrence of life on an exo-earth candidate with a minimum past quiescent stellar UV flux, focusing on the prebiotically interesting \gls{NUV} range from \SIrange{200}{280}{\nano\meter}. \todo[inline]{SUKRIT: got a good reference for this?}  %~\citep{RanjanSasselov2016}.?
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received such radiation exceeded a minimum flux $F_\mathrm{NUV, min}$.
We further require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}, and the planet to be within its momentary \gls{HZ} during this entire period.

>>>>

\subsection{H3: Life only originates on planets with particular UV irradiance}
\todo[inline]{\citet{Guenther2020} relate U-band energy to bolometric flux.}
\todo[inline]{OPTIONAL: ``We further test the scenario of a linear correlation of past UV flux and biosignature occurrence rate.
This test requires the detection of multiple biosignatures.''
~\\
Test for negative correlations as well?}
Our third theoretical experiment is to test the UV irradiance requirement (Sect.~\ref{sec:predictions:uv}) by relating the occurrence of life on an exo-earth candidate with a minimum past quiescent stellar UV flux, focusing on the prebiotically interesting \gls{NUV} range from \SIrange{200}{280}{\nano\meter}. \todo[inline]{SUKRIT: got a good reference for this?}  %~\citep{RanjanSasselov2016}.?
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received such radiation exceeded a minimum flux $F_\mathrm{NUV, min}$.

\subsubsection{Semi-analytical analysis}
First, we apply a Bayes Factor Design Analysis~\citep{Schoenbrodt2018} to assess the expected probabilities of obtaining true negative or true positive evidence for the hypothesis above, as well as the probability for misleading or inconclusive evidence.

\subsubsection{Survey simulations with Bioverse}
To model the sensitivity of the information gain of a proposed mission to sample selection and survey strategy, we now conduct survey simulations with Bioverse using different sample sizes and survey strategies.
We again require that life occurs only on planets with sufficient past UV irradiation exceeding $F_\mathrm{NUV, min}$.
Further, we require this flux to have lasted for a minimum duration $\Delta T_\mathrm{min}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}, and the planet to be within its momentary \gls{HZ} during this entire period.
